\documentclass[12pt]{article}

\usepackage{fancyhdr}


\usepackage{amsfonts, amsmath, amsthm, amssymb, graphicx, verbatim}
\usepackage[margin=1.0in]{geometry}
\usepackage{booktabs} % Top and bottom rules for table
\usepackage[font=small,labelfont=bf]{caption} % Required for specifying captions to tables and figures
\usepackage{amsfonts, amsmath, amsthm, amssymb, graphicx, verbatim} % For math fonts, symbols and environments
\usepackage{wrapfig} % Allows wrapping text around tables and figures
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{thm-restate}
%\usepackage[backend=bibtex]{biblatex}


\usepackage[colorlinks=true,breaklinks=true,bookmarks=true,urlcolor=blue,
citecolor=blue,linkcolor=blue,bookmarksopen=false,draft=false]{hyperref}
\usepackage{url}
\usepackage{float}
\usepackage{enumitem}

\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
	\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\jessie}[1]{\mynote{blue}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{blue!20!white}{JF: #1}}
\newcommand{\gabe}[1]{\mynote{purple}{[GA: #1]}}
\newcommand{\gabet}[1]{\mytodo{purple!20!white}{GA: #1}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{\textcolor{gray}{#1}}}
\newcommand{\future}[1]{}%\mytodo{blue!20!white}{\textcolor{gray!50!black}{FUTURE: #1}}}
\ifnum\Comments=1               % fix margins for todonotes
\setlength{\marginparwidth}{1in}
\fi

\pagestyle{fancy}
\lhead{Jessica Finocchiaro and Gabriel P. Andrade}
\rhead{CSCI 5423- Project proposal}


\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\myderiv}[1]{\tfrac{d}{d#1}} % \partial_{#1}
\newcommand{\myrderiv}[1]{\tfrac{\,d^+\!\!}{d#1}} % \partial_{#1}
\newcommand{\dz}{\myderiv{z}}
\newcommand{\dx}{\myderiv{x}}
\newcommand{\dr}{\myderiv{r}}
\newcommand{\du}{\myderiv{u}}
\newcommand{\rdx}{\myrderiv{x}}

%m upper and lower bounds
\newcommand{\mup}{\overline{m}}
\newcommand{\mlow}{\underline{m}}


% alphabetical order, by convention
\newcommand{\C}{\mathcal{C}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Y}{\mathcal{Y}}
\renewcommand{\P}{\mathcal{P}}

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}


\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}
\DeclareMathOperator*{\sgn}{sgn}


\newtheorem{definition}{Definition}	 
\newtheorem{proposition}{Proposition}	 
\newtheorem{condition}{Condition}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}



\begin{document}

%1-2 page proposal
%description of the problem and its significance
%description of background and related work
%plan of execution along with list of weekly milestones
%short bibliography

\section{Problem and motivation} 
Collective transport of objects by multi-agent systems is a difficult problem that often requires we choose between centralized and decentralized solution; accepting both the pros and cons of the chosen approach \cite{rubenstein2013collective, chen2015occlusion, mccreery2016collective}. 
This unfortunate compromise is only made more difficult by factors often present in scenarios where collective transport is required such as the goal being visually occluded, agents being restricted by hardware constraints, communication is limited, etc.


As Gelblum et al.~\cite{gelblum2015ant} points out, the \emph{Paratrechina longicornis} ants are able to collectively transport food items in a decision making process that is intermediate between the sole decisions of a few ants and every ant making their own decision.
In collective transport, contradicting forces on the transported object can lead to stagnation, so the ability to reach a consensus is crucial.



Liquid democracy is a system of decision making that lies as a happy compromise between true and representative democracy.
True democracy, in which everyone votes on every decision to be made, is often difficult to implement in practice, and agents are often uninformed on the vote.
However, in representative democracy, agents do not have the ability to voice their own opinion on topics they really care about.
Instead, in a liquid democracy, agents are given the choice to delegate their vote to another agent-- increasing their ``voting power,'' or to vote on their own behalf.


Liquid democracy has been implemented in a handful of political parties globally, with the most notable of these being the German Pirate Party\footnote{\url{http://techpresident.com/news/wegov/22154/how-german-pirate-partys-liquid-democracy-works}}.
However, in political systems, the mechanism to delegate votes must be chosen carefully, otherwise the emergence of a dictatorship could easily arise- as happened in the GPP.
We hope to combine centralized and decentralized decision making processes in our model by using mechanisms inspired by liquid democracy for the goal of collective transport.
One struggle of liquid democracy in social practices is avoiding the emergence of a dictatorship.
However, this is a virtue for us, as informed agents will become the dictator in our setting.


\section{Background and related work}

A variety of papers~\cite{leonard2012decision, berdahl2013emergent, couzin2011uninformed} study consensus in path planning by animal groups.
In particular, we base our work more heavily on the following papers:

\begin{itemize}
	\item Gelblum et al.~\cite{gelblum2015ant} studies the ability of ants to work as a team to transport a cheerio.
	In their paper, they track each ant's movement in a video to distinguish the path of informed ants that don't carry the burden of the cheerio, and carrier ants that tend to follow the informed ants.
	They also develop a theoretical model to accompany their data that models pulling and pushing ants.
	\item Peters and Adamou~\cite{peters2015evolutionary} discusses the apparently contradictory presence of cooperation in evolution.
	While the world is competitive (after all, ``survival of the fittest'' is a term we all know for a reason), this paper emphasizes the cooperation required and found in evolution.
	They point out that cooperation is observed in nature because those who do outgrow those who don't cooperate.
	(Sidebar from Jessie: I just had a paper published that supports this sentiment in~\cite{finocchiaro2019evolving}.)
	
	\item Kirman~\cite{kirman2016ants} proposes replacing standard utility-based macroconomic models with agent-based models in which agents behave by a set of local rules.
	He cites economists who compare the economy to the flight of a bumblebee; by most models, it does not make sense.
	He argues that we should adjust our models to accommodate the actual, observed behavior in the actual economy.
	This paper, like many studied in class, draws conclusions about human systems based on observations of animal behavior.
	In our paper, we take the opposite approach, where we look at an economic model and evaluate possible similarities to ant colonies.
\end{itemize}

\section{Implementation ideas}
In our project, we plan to simulate a population of agents that are placed on a $m \times m$ triangular lattice and simulate their efficiency in transporting a $k_o \times k_o$ object towards a given goal.
Agents should have varying amounts of knowledge about the location of their destination, like the model of Couzin et al.~\cite{couzin2005effective}.
In an environment with discretized time, at each time step $t$, each agent chooses an action from the set $A_i \subseteq A := \{$Up, Down, Left, Right, $a_1, \ldots, a_{i-1}, a_{i+1}, \ldots, a_n \}$.
The vote $a_j$ is the delegation of one's vote to neighbor $j$, and a directional action is the agent casting a vote in that direction on behalf of every agent who delegated to them, including themself.

We also equip each agent with a confidence set $C$ that has to distinguish agents from one another.
For example, this set could be $\{$Carrier, Clueless, Volunteer, Informed $\}$, where we assume agents carrying the object aren't able to search for the goal, hence carrier being its own category.

Our potential voting mechanism is to delegate our vote to our neighbor with the ``highest'' confidence.
If agents are informed (i.e. they can see the goal or can see an informed agent), they vote on their own behalf in the direction of the goal.
If the agent is a volunteer and cannot see an informed agent, they will vote in a direction chosen from a (possibly  fixed) probability distribution.
A clueless agent will delegate their vote to their neighbor who broadcasts the highest confidence, and carriers delegate their vote to anyone in front of them.

At each time step $t$, consider the following sequence of subroutines:
\begin{enumerate}
	\item Broadcast your confidence to the world.
	\item Choose an action from $A_i$
	\item ``Communicate'' your vote to neighbors if necessary
	\item Move in the direction your vote went
	\item Update your confidence
\end{enumerate}

%We plan to use three ``types'' of ant: Scouts who are searching for the destination, leaders who have an idea where the destination is but are helping carry the object, and followers, who are less educated.
%At each time step $t$, each ant that is carrying the object (i.e. leaders and followers, but not scouts) will cast a vote on which one of 8 directions to move.
%As standing still is undesirable, we assume that ants would rather move in an undesired direction than stand still.
%
%As ants are carrying the object, they become less informed about their location relative to the goal over time.
%We plan to incorporate some diminishing knowledge decay, so that, as leaders continue to carry the object, they may turn into followers if they don't leave soon enough to scout.
%In our model, we assume that ants can be ``tagged out'' by a scout, who then takes their place carrying the object, but as a leader- regardless of who they tagged out.
%
%When the group is deciding the direction to move in, leaders and followers are the only ants voting, as scouts are not currently attached to the object being transported, nor the ants transporting it, so there is no way for scouts to communicate to leaders and followers until the scout returns.
%Leaders and followers both delegate their vote to a neighbor with probability $p$, and make their own vote with probability $(1-p)$.
%Since leaders are more informed than followers, the probability of delegation $P(delegate|leader) < P(delegate|follower)$.
%Any scout that returns to the object should return as a leader since they are more knowledgable about the location of the goal.
%
%Another consideration we have to make is the line of vision for an ant- particularly the scouts.
%Supposing our $n$ ants are on an $m \times m$ grid, if the ants have a \jessie{conic? then we have to worry about orientation} line of sight of ``length'' $m$, then every ant should be able to see the target and vote to move in the most direct direction toward the goal.
%However, if ants can only see the $1$ square around them, then almost no ant would have any information about the location of the target, and we conjecture the path would look like a random walk.


\section{Weekly Milestones}
\begin{itemize}
\item By Wednesday, March 20-- Write the project proposal
\item By Sunday, March 24-- Design the algorithm
\item By Sunday, March 31-- Implement algorithm for each ant
\item By Sunday, April 7-- Get simulations running
\item By Sunday, April 14-- Analyze results
\item By Sunday, April 21-- Finish project implementation
\item By Sunday, April 28-- Write up paper and make presentation
\end{itemize}

\section{Future Work}
\begin{itemize}
\item Move to a continuous setting
\item Finding object then transporting it
\item Multiple objects to transport
\item Handling Byzentine agents
\item Make the line of sight conic
\end{itemize}


\bibliographystyle{ieeetr}
\bibliography{refs}


\end{document}